Quantifying the manageability of pollination networks in an invasion context

### 2017-06-16 paper/cover-letter.tex
Update cover letter for Proceedings B

\begin{letter}{
       %\vspace*{20pt}
       Prof. Tim Coulson\\
       Editor in Chief\\
       Ecology Letters}

\opening{Dear Proffesor Coulson,}

We are submitting the manuscript entitled ``Biotic invasions reduce the manageability of pollination networks'' to be considered for publication at \emph{Ecology Letters}.

@@

Multiple empirical observations have suggested that the structural changes caused by invasions may lead to increased ecosystem resilience. 
Our study is the first to use empirical data to provide theoretical support for this idea. 
Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system. 
Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.

>>>>

\begin{letter}{
       %\vspace*{20pt}
       Prof. Spencer Barret\\
       Editor in Chief\\
       Proceedings of the Royal Society B}

\opening{Dear Proffesor Barrett,}

We are submitting the manuscript entitled ``Quantifying the manageability of pollination networks in an invasion context'' to be considered for publication at \emph{Proceedings B}.

@@

Multiple empirical observations have suggested that the structural changes caused by invasions may lead to changes on ecosystem resilience. 
Our study is the first to use empirical data to provide theoretical support for this idea. 
Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system. 
Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.
